Technical Report

### 2024-08-14 Reports/tech_report1.tex

>>>>

\subsection*{Layer 5, both in layer 1 and layer 3, separately}

In this test we choose 30 nodes in layer 1 and 30 nodes in layer 3. Again they are grouped 5 by 5. We use $A,a,a'$ to denote nodes in layer 1, and use $B,b,b'$ to denote nodes in layer 3.

And we define:  $$Imp^A(B)=MILP_{A}-MILP_{A\cup B}.$$ We still use $Imp(B)$ for $Imp^{\emptyset}(B)$.

The aim of this section is to check, how can we compute $Imp^A(B)$?

\subsubsection*{Based on $Imp^A$}

If we use $Imp^A(b)$ to compute $Imp^A(B)$, then the accuracy is very high: $$Imp^A(B)\approx\sum_{b\in B} Imp^A(b).$$

The average of $\dfrac{\sum_{b\in B} Imp^A(b)}{Imp^A(B)}$ is 1.0012830624338422, and the standard deviation over all cases is
0.263 \%.

However, this is not very useful since we must face more than one possible $A$ and we cannot compute $Imp^A(b)$ every-time.

\subsubsection*{Based on $Imp$}

In this case, the accuracy is relatively low: The average of $\dfrac{\sum_{b\in B} Imp(b)}{Imp^A(B)}$ is 0.8943970938704465, and the standard deviation over all cases is
4.26 \%.

However, this does not mean that $Imp(b)$ is useless. If we group $A$ by $\#(A)$ and compute the standard deviation group by group, then we will find it is much smaller. We use $\mu(n)$ to denote the average number of all $\dfrac{\sum_{b\in B} Imp(b)}{Imp^{A}(B)}$ that $\#(A)=n$.

For $n$ in $0$ to $6$, $\mu(n)$ and corresponding standard deviations are:

0.995, 0.30\%

0.957, 0.98\%

 0.923, 1.68\%

 0.893, 2.25\%

 0.865, 2.71 \%

 0.839, 3.08 \%

 0.814, 3.45 \%

It is reasonable that the average goes smaller and smaller.

If we look at the absolute value of $Imp$, we will find that for almost all $A,B$, $$|Imp^A(B)-\frac{1}{\mu(\#(A))}(\sum_{b\in B} Imp(b))| < 0.01,$$ and this is usable. At least that we can still use $Imp(b)$ to sort nodes in layer 3 for any $A$.

\section{Layer 7, large test 0}

This is similar to the tests in last section but more simpler. We choose 35 nodes by our algorithm in layer 1, layer 3 and layer 5 separately, and group them 5 by 5 nodes.

The difference is that, we do not consider all $2^{7+7+7}$ cases, but only consider about $7\times 7 \times 7$ cases: first $m\times 5$ nodes in layer 1, first $n\times 5$ nodes in layer 3 and first $l \times 5$ nodes in layer 5.

We can count the information by node in layer 7. For example, when $n+m+l=10$ (50 nodes), we can count the best $[n,m,l]$ combinations for every node: the average is $[3.92,2.02,4.06]$. For $n+m+l=12$ (60 nodes), the average is $[4.92,2.81,4.27]$. This is consistent with our previous observations.

However, although the average values are consistent with previous result, for a single node, the case can be very different: the deviation of $n,m$ is about 2, and there are a few nodes for which $m=7$ is the best.
